\section{Introduction}
\label{sec:intro}

The precise understanding of the electroweak symmetry breaking 
mechanism is an important cornerstone of the LHC physics 
programme. 
Different realisations of the electroweak sector or new physics 
coupling to electroweak gauge bosons will yield to deviations 
compared to the Standard Model prediction. 
New physics effects can conveniently be described in terms of 
an effective theory where new heavy degrees of freedom are 
integrated out and deviations from the Standard Model are 
parametrised by higher dimensional operators 
\cite{Weinberg:1978kz,Weinberg:1979pi}. 
Higher dimensional operators can lead to deviations in triple 
and quartic gauge couplings. Moreover, new vertices 
(e.g. $\gamma\gamma\gamma$, $Z\gamma\gamma$) that do not 
exist in the Standard Model can appear. 
The class of processes that involve a pair of photons in 
association with another vector boson allows to measure 
deviations in triple and quartic gauge couplings and is 
therefore a particularly interesting class of processes. 
Consequently both ATLAS and CMS have measured these types of 
processes and derived constraints on anomalous gauge couplings 
\cite{Aad:2016sau,Sirunyan:2017lvq,Aad:2015uqa,Aad:2015bua}. 

In this paper we calculate the next-to-leading order QCD and 
electroweak corrections to the processes $\gamma\gamma\gamma$, 
$\gamma\gamma e^{+} e^{-}$ and $\gamma\gamma e^{-} \bar{\nu_e}$. 
For the latter two, all possible off-shell contributions of 
intermediate vector bosons are taken into account. 
The QCD corrections to these processes have already appeared 
in the literature 
\cite{Bozzi:2011en,Campbell:2012ft,Bozzi:2011wwa}. 
For a more complete picture of the higher order effects we 
recompute them for a centre of mass energy of 
13\,TeV, and supplement them with the next-to-leading order 
electroweak corrections. 
Although the electroweak corrections are much smaller at the level 
of the total cross section compared to the NLO QCD corrections 
they are particularly important when deriving limits on 
anomalous couplings. 
The effects of higher dimensional operators increase in the 
high energy tails of differential distributions and lead to a 
change of the shapes. And it is in the same region where the 
Sudakov logarithms from the electroweak corrections will play 
an essential role as well.

The paper is organized as follows. 
In Section \ref{sec:setup} we describe the calculational setup 
that has been used to obtain our numerical result which we are 
going to discuss in Section \ref{sec:results} before we 
conclude in Section \ref{sec:conclusions}.
 